\pagestyle{fancy}
\fancyhead[L]{\ungaramond\small\textbf{}}
\fancyhead[C]{}
\fancyhead[R]{\ungaramond\small\textbf{}}
\fancyfoot[L]{\ungaramond\small\textbf{Ridha Bouazizi}}
\fancyfoot[C]{}
\fancyfoot[R]{\ungaramond\small\textbf{Page \thepage\ sur\ \pageref{LastPage}}}
\renewcommand{\headrulewidth}{1.7pt}
\renewcommand{\headrule}{\hbox to\headwidth{\color{gray}\leaders\hrule height \headrulewidth\hfill}}
\renewcommand{\footrulewidth}{1.7pt}
\renewcommand{\footrule}{\hbox to\headwidth{\color{gray}\leaders\hrule height \footrulewidth\hfill}}
\pagenumbering{arabic}
\phantomsection\addcontentsline{toc}{chapter}{General topic } % inclure dans TdM
\begin{center}
\ungaramond{\textbf{\LARGE{General topic }}}
\fancyhead[R]{\ungaramond\small\textbf{General topic }}

\end{center}
\vspace{0.8cm}
\setcounter{page}{1}


Our project aims to put in place a complete Platform as a Service (PaaS) environment in the cloud and implement the standard DevOps best practices to improve software delivery and operational efficiency. 

Cloud computing has revolutionized the way we deploy and manage software applications, offering greater flexibility, scalability, and cost savings. 

PaaS is a cloud-based service that provides developers with a platform to build, deploy, and manage applications without the need for infrastructure management. PaaS allows organizations to focus on developing and delivering software applications rather than managing the underlying infrastructure. 

DevOps is a set of practices that emphasizes collaboration and communication between development and operations teams to improve software delivery and operational efficiency. DevOps aims to break down the silos between development, operations, and other IT functions to create a more efficient and effective software delivery pipeline. 

Our project will focus on implementing the Agile DevOps method to improve collaboration between development and operations teams, automate software delivery pipelines, and increase the speed of software delivery. We will use a variety of tools and technologies, including containerization, continuous integration and deployment, and infrastructure automation to achieve our goals. 

We believe that our project will provide a valuable contribution to the field of cloud computing and DevOps by demonstrating how the Agile DevOps method can be used to improve software delivery and operational efficiency in PaaS environments. 

We look forward to sharing our results and findings with the community and contributing to the ongoing evolution of these important fields.
