\thispagestyle{empty}
\thispagestyle{empty}
\begin{center}
\ungaramond{\textbf{\LARGE{Dedications}}}
\end{center}
\vspace{0.8cm}

I would like to dedicate this end-of-studies project to all the people who supported me throughout my professional and personal career. I am grateful to the following individuals: 

My parents for their unwavering love and support throughout my life. I owe them for everything they have done for me, and I am grateful to have them as family. 

My brother, Mr. Rafick Bouazizi, who sponsored my education, for his financial and moral support throughout my academic journey. Without his help, I would not have been able to achieve my educational goals. 

All my family members for their unconditional love and support throughout my life. I am grateful to have them as family and I am grateful for their support and encouragement. 

My friends for their support, friendship, and encouragement throughout my academic and professional journey. Their support and presence helped me through the ups and downs of life and to persevere in my efforts. 

I am grateful to all these people for their support and encouragement, and I dedicate this project to them with gratitude and appreciation.
\begin{flushright}
\textbf Ridha Bouazizi
\end{flushright}

\newpage
\thispagestyle{empty}
\begin{center}
\ungaramond{\textbf{\LARGE{Dédicaces}}}
\end{center}
\vspace{0.8cm}

Je voudrais dédier ce travail de fin d'études à toutes les personnes qui m'ont soutenu tout au long de mon parcours professionnel et personnel. Je suis reconnaissant envers les personnes suivantes : 

Mes parents pour leur amour et leur soutien indéfectibles tout au long de ma vie. Je leur suis redevable pour tout ce qu'ils ont fait pour moi et je suis reconnaissant de leur avoir comme famille. 

Mon frère, M. Rafick Bouazizi, qui a sponsorisé mon éducation, pour son soutien financier et moral tout au long de mon parcours universitaire. Sans son aide, je n'aurais pas pu atteindre mes objectifs éducatifs. 

Tous les membres de ma famille pour leur amour et leur soutien inconditionnels tout au long de ma vie. Je suis reconnaissant de les avoir comme famille et je leur suis reconnaissant pour leur soutien et leur encouragement. 

Mes amis pour leur soutien, leur amitié et leur encouragement tout au long de mon parcours universitaire et professionnel. Leur soutien et leur présence m'ont aidé à traverser les hauts et les bas de la vie et à persévérer dans mes efforts. 

Je suis reconnaissant envers toutes ces personnes pour leur soutien et leur encouragement, et je leur dédie ce travail avec gratitude et reconnaissance.

\begin{flushright}
\textbf Ridha BOUAZIZI
\end{flushright}